---
title: "theCLT"
author: "Carmen Ramos-Caminos"
date: '6/23/2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?  
The Plot is Bi-modal. It has two peaks that are about the same in size.   

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?   
This graph appears to me to be trimodal with a central peak.  

Do this again for 4 random samples  
```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
print(mean(x.avg))
print(sd(x.avg))
```

Then again for 9 random samples   
The graph appears to be trimodal with one central peak

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
print(mean(x.avg))
print(sd(x.avg))
```

then 16 random samples    
This graph appears to be unimodal.

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
print(mean(x.avg))
print(sd(x.avg))
```

finally for 36 random samples    
This graph appears to be unimodal.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
print(mean(x.avg))
print(sd(x.avg))
```

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.  
Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.  


Then submit the link to your github project  to canvas to complete this assignment.