---
title: "theCLT"
author: "Carmen Ramos-Caminos"
date: '6/23/2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?  

The Plot is Bi-modal. It has two peaks that are approximatley the same in size.  The mean is 50.4003 with a standard deviation of 41.75955

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?      

This graph appears to be trimodal with a central peak. The graph shows two peaks on either side of the central peak. The mean is 51.4985 with a standard devistion of 29.4555

Do this again for 4 random samples  
```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
print(mean(x.avg))
print(sd(x.avg))
```

The graph appears to be multimodal with one central peak with additional peaks on either side. The peaks appear symetrical. The mean is 49.876 and the sdtandard deviation is 20.51154.  

Then again for 9 random samples   

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
print(mean(x.avg))
print(sd(x.avg))
```

This graph appears to be unimodal and symetrical. The mean is 51.38078 and the standarddeviation is 14.15083.  

then 16 random samples    

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
print(mean(x.avg))
print(sd(x.avg))
```

The graph apears to be unimodal. The mean of this graph is 50.28794 with astandad deviation of 10.58187.

finally for 36 random samples    

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
print(mean(x.avg))
print(sd(x.avg))
```

This graph is unimodal. The mean is 49.80406 and the standadrd deviation is 6.87269.

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.  
Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.  


Then submit the link to your github project  to canvas to complete this assignment.